Effect of quality-adjusted production function inputs

### 2015-05-04 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Creating graphs.

>>>>

\begin{table} \caption{Unadjusted time-series variables.} 
\label{tab:unadjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal           & UK                 \\
      \midrule
      Output      & \Sexpr{y_PT}       & \Sexpr{y_UK}       \\
      Capital     & \Sexpr{k_PT_unadj} & \Sexpr{k_UK_unadj} \\
      Labor       & \Sexpr{l_PT_unadj} & \Sexpr{l_UK_unadj} \\
      Energy      & \Sexpr{e_PT_unadj} & \Sexpr{e_UK_unadj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

\begin{table} \caption{Quality-adjusted time series variables.} 
\label{tab:quality_adjusted_variables} 
  \begin{center}
    \begin{tabular}{r l l} 
      \toprule
      Variable    & Portugal         & UK               \\
      \midrule
      Output      & \Sexpr{y_PT}     & \Sexpr{y_UK}     \\
      Capital     & \Sexpr{k_PT_adj} & \Sexpr{k_UK_adj} \\
      Labor       & \Sexpr{l_PT_adj} & \Sexpr{l_UK_adj} \\
      Energy      & \Sexpr{e_PT_adj} & \Sexpr{e_UK_adj} \\
      \bottomrule
    \end{tabular}
  \end{center}
\end{table}

<<Historical Data, fig.pos="H", fig.align='center', fig.width=6.6, fig.height=7, fig.cap="Historical data.">>=
mdata <- melt(historicalData, 
              measure.vars = c(as.character(y_PT), 
                               as.character(k_PT_unadj), as.character(l_PT_unadj), as.character(e_PT_unadj),
                               as.character(k_PT_adj), as.character(l_PT_adj), as.character(e_PT_adj),
                               as.character(y_UK), 
                               as.character(k_UK_unadj), as.character(l_UK_unadj), as.character(e_UK_unadj),
                               as.character(k_UK_adj), as.character(l_UK_adj), as.character(e_UK_adj)), 
              variable.name = "variable",
              value.name = "value")
historicalPlot(mdata, 
               mapping=aes(x=Year, y=value, group=variable, linetype=variable), 
               facet_formula = Country ~ Source, 
               line_types = c(1:11)) + 
  xlab("") + 
  ylab("Indexed (1960=1)")
@
